---
title: "Roll the Dice"
author: "Anna"
date: "10/6/2021"
output: 
  html_document: 
    theme: cerulean
    toc: true
    toc_float: true
  
---

```{r setup, include=FALSE}

```

In this simple project, I am simulating the rolling of two dice. 

## Create the dice

```{r }
#create a die, this is an object that R will save for use later
die <- 1:6
```

## Simulate the roll of 2 dice

To simulate the roll of 2 dice I use the 'sample' function.

```{r}
#sample a number from 2 dice with replacement
dice <- sample(die, 2, replace = TRUE)
```

Use inline code to put the result of my sampling into the sentence below in my output doc.:

When I simulate rolling the dice, I get a: `r dice`

## Sum the result

Now, I will sum the numbers on my two dice:
```{r}
#sum the two results
total<- sum(dice)
```

The sum of my two dice is: `r total`

## Create one function for the simulation

I am going to make the rolling of the dice and summing the two into a function called roll. Here is the code: 

```{r echo=TRUE}
#make the dice rolling a function
roll<- function () {
  die<- 1:6
  dice<- sample(die, 2, replace=TRUE)
  sum(dice)
}
```

## Roll the dice

```{r echo=TRUE}
roll1<- roll()
```

I rolled the dice again, using the roll function. I got a total of: `r roll1`

```{r}
roll2<- roll()
```

And, I rolled it again. This time I got: `r roll2`

## Probability of outcomes

What is the probability of getting 1 of the 12 different possible totals from the two dice? Note, the probability of each of the possible totals are not the same. So, it is not just 1/12.

```{r }
#create a vector of the possible totals from rolling two dice
totals<- c(outer(1:6, 1:6, "+"))

#Create a vector of the unique possible totals
Total<- unique(totals)

#How many times does each possible outcome occur?
freqs<-table(totals)

#What is the probability of each possible outcome?
props<-data.frame(prop.table(freqs))

#create a table with each possible outcome and each probability
SummaryTable<-data.frame(props)
colnames(SummaryTable)<-c('Total','Probability')
```

Here is the Summary Table with the possible total and it's probability:

```{r echo=FALSE, comment=NA}
print(SummaryTable, row.names=FALSE)
```

